%-------------------------
% Resume in LaTeX
% Author : Anson Chan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{comment}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[1]{
  \item[$\circ$]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemPtHeader}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumePublicationItem}[1]{
  \item\small{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \small#3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Fromatting for Eduaction Section
\newcommand{\resumeEducationSubheading}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \vspace{-1pt}
      \small#3 & \small #4 \\
      \vspace{-1pt}
      \small#5 & \small #6 \\
      \small#7 & \small #8 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-20pt}
}



\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=20pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItemListStart}{\begin{itemize}[leftmargin=10pt]}
\newcommand{\resumeSubItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumePublicationListStart}{\begin{enumerate}[leftmargin=0.15in]}
\newcommand{\resumePublicationListEnd}{\end{enumerate}\vspace{-16pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{comment}
%----------HEADING----------
\begin{center}
  {\Huge \bfseries WaiYan (Anson) Chan} \\ \vspace{0.5pt}
  %123 Street Name, Town, State 12345 \\ \vspace{1pt}
  \href{mailto:ans0nchan@outlook.com}{\raisebox{-0.1\height}\  ans0nchan@outlook.com}~
  $|$
  \small \raisebox{-0.1\height}\ 630-210-1557~
  $|$
  \href{wchan29.github.io}{\raisebox{-0.1\height}\ Personal Website: wchan29.github.io} ~
  \vspace{-8pt}
\end{center}
\end{comment}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE WaiYan(Anson) Chan}} & E-mail: \href{mailto:ans0nchan@outlook.com}{$\mathtt{ans0nchan@outlook.com}$}\\
  Ph.D. Candidate, \href{wchan29.github.io}{$\mathtt{wchan29.github.io}$} & Mobile: (630)210-1557 \\
  \vspace{-20pt}
\end{tabular*}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeEducationSubheading
{University of Wisconsin-Madison}{Madison, WI}
{Ph.D. in Electrical and Computer Engineering}{Present}
{M.S. in Electrical and Computer Engineering}{June 2024}
{B.S. in Mechanical Engineering}{December 2021}
\resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
\begin{multicols}{3}
  \begin{itemize}[leftmargin=0.15in, itemsep=-5pt, parsep=4pt]
    % ------ INSERT COURSEWORK HERE------
    \item\small Dynamics and Control of AC Drives
    \item EM Design of AC Machines
    \item Redesign and Prototype Fabrication
    \item Power Electronic Circuits and Lab
    \item Automatic Controls Lab
    \item Finite Elements
          % ------ INSERT COURSEWORK HERE------
  \end{itemize}
\end{multicols}
\vspace*{1.0\multicolsep}

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Precision Mechatronics and Control Lab - WEMPEC}{Aug. 2024 -- Present}
{Graduate Research Assistant, Ph.D. - \textit{Advisor: Lei Zhou}}{Madison, WI}
\resumeSubheading
{Severson Research Group - WEMPEC}{Aug. 2022 -- Jun. 2024}
{Graduate Research Assistant, M.S. - \textit{Advisor: Eric L. Severson}}{Madison, WI}
\resumeItemListStart
\resumeItem{\textbf{Additively Manufactured (AM) Stator Housing for High-Speed Bearingless Generator}}
\resumeSubItemListStart
\resumeSubItem{Developed and fabricated AM housing with integrated cooling channels for a 100kW, 80kRPM high-speed twin bearingless generator in a microturbine-based CHP generation system.}
\resumeSubItemListEnd
\resumeItem{\textbf{Bearingless Machines (BSPM) for Aerial E-Turbocharger Application}}
\resumeSubItemListStart
\resumeSubItem{Conducted structural and modal analysis to validate rotor design by identifying critical speed and rotor stress.}
\resumeSubItem{Modeled and conducted FE analysis of an 8kW 4-DOF twin-stator BSPM, along with component fabrication.}
\resumeSubItem{Facilitated the development of multi-physics modeling framework for BSPM and created Python scripts for evaluating machine constants and coil inductances in JMAG.}
\resumeSubItemListEnd
\resumeItemListEnd
\resumeSubheading
{Wisconsin Electric Machinery and Power Electronics Consortium}{Sep. 2019 – Dec. 2021}
{Undergraduate Researcher}{Madison, WI}
\resumeItemListStart
\resumeItem{Prototyped a desktop size dynamometer setup capable of characterizing electric machines rated up to 10 N-m of torque and 3000 RPM. Reduced the original setup volume by 35\%.}
\resumeItem{Collaborated with a team of graduate researchers to prototype a modular terminal box for powering a 200 kW NASA prototype machine. Responsible for sourcing parts and creating CAD models. }
\resumeItem{Fabricated BSPM machines by producing stator slot windings and machining components used in the assembly. }
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-13pt}

%-----------WORK EXPERIENCE-----------
\section{Industry Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Milwaukee Tool}{Jan. – Aug. 2022}
{NPD Mechanical Design Engineer}{Brookfield, WI}
\resumeItemListStart
\resumeItem{Conducted FE analysis on BLDC machines of various sizes and winding configurations, recommended optimal designs for product development using Pugh Matrix for informed and cost-effective solutions.}
\resumeItem{Assessed power tool performance requirements through the collection and analysis of motor thermal characteristics and power output data from competitor products.}
\resumeItemListEnd
\vspace{-5pt}
\resumeSubHeadingListEnd


%-----------PROJECTS and SKILLS-----------
\section{Projects \& Skills}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{eMach} $|$ \emph{Open-Source Python Machine Modeling and Optimization Framework}}{2022 - Present}

% \resumeProjectHeading
% {\textbf{Compact Low Voltage Induction Machine with 3D Printed Housing} $|$ \emph{ME Senior Design}}{2021}

\resumeProjectHeading
{\textbf{UW CoE Undegraduate Learning Center} $|$ \emph{Tutor, Physics and Engineering Statics}}{2018-19}

\resumeProjectHeading
{\textbf{Wisconsin Racing Electric} $|$ \emph{Chassis Team Member}}{2018-21}

\resumeSubHeadingListEnd

\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
        \textbf{Hands-on}{: Electric Machine Fabrication, Component Machining and Assembly, CAD Design and Drafting, GD\&T} \\
        \textbf{Tools}{: Python, Git, SolidWorks, NX, ANSYS, MATLAB / Simulink, Altium,  LabView, MAGNET, FEMM, JMAG, \LaTeX } \\
        }}
\end{itemize}
\vspace{-16pt}

%-----------Publications-----------
\section{Publications}
\resumePublicationListStart
\resumePublicationItem{T. Noguchi, N. Petersen, \textbf{W. Chan}, L. Rapp, E. Severson,  “Bearingless Motor/Generator Applications in sCO\textsubscript{2} Power Cycles,” \textit{The 8th Internationl Supercritical CO\textsubscript{2} Power Cycles Symposium, San Antonio, TX, USA, 2024 (Accepted)}}

\resumePublicationItem{T. S. Slininger, \textbf{W. Chan}, E. L. Severson, and B. Jawdat, "An Overview on Passive Magnetic Bearings," \textit{2021 IEEE International Electric Machines \& Drives Conference (IEMDC), Hartford, CT, USA, 2021}}
\resumePublicationListEnd
\vspace{5pt}





\end{document}
